---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(auditr)
```


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



```{r}
plastic_proportions(countries = c("Argentina", "Canada"), years = 2019)
```

This should make a summary table of the proportions of each plastic type over all companies found in the Argentina audits for the year 2019.


```{r}
rate_ify2()
```



```{r}
density_plotter()
```

This function should plot the total plastic count versus the gdp for each country for the year 2020. There should be one point for each country in the data.


```{r}
bubble_plotter(countries = c("China", "United States of America", "Nigeria"))
```

This function should make a bubble plot for the chosen countries showing the total
plastic waste vs the country's GDP with bubble size as the population of the country for 
the years 2019 and 2020.


```{r}
load_data()
```

This function loads in the final merged dataset that was used in creating this analysis.


```{r}
auditr:::clean_data()
```



```{r}
stat_analysis()
```


