---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(auditr)
```

## Load data

```{r}
dat <- load_data()
head(dat)
```

This function loads the merged plastic pollution dataset stored in the package.

## Clean data

```{r}
cleaned <- clean_data()
head(cleaned)
```

This function cleans the plastic pollution data by replacing missing plastic type counts with zero, creating a row level total, and standardizing country names.

## Plastic proportions

```{r}
plastic_proportions(countries = c("Argentina", "Canada"), years = 2019)
```

This function creates a table showing the proportion of each plastic type for selected countries and years.

## Rate columns

```{r}
rate_ify2(
  df = dat,
  numerators = hdpe:pvc,
  denominator = grand_total
)
```

This function converts selected plastic count columns into rates using a denominator column.

## Density plot

```{r}
density_plotter(
  data = dat,
  selected_year = 2020,
  cutoff = 2000,
  chosen_types = c("hdpe", "pvc", "other")
)
```

This function creates a density ridge plot comparing plastic audit amounts across income groups.

## Bubble plot

```{r}
bubble_plotter(countries = c("China", "United States Of America", "Nigeria"))
```

This function creates a bubble plot comparing plastic pollution and GDP for selected countries.

## Statistical analysis

```{r}
stat_analysis(fixed_vars = c("Population", "year", "region"))
```

This function fits a mixed-effects model and returns a formatted Type III ANOVA table.
